---
title: "Regressions results - Long term beliefs"
author: "(Using previous record stage emotions)"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---


$B_{t,i}-B_{t-1,i} = C_{i} + \beta_1(P_{t}-P_{t-1}) + \beta_2(B_{t-1,i}-B_{t-2,i}) + \beta_3(B_{t-1,i}-P_{t-1})$


(Fixed effects regression model)
(Periods 2-14 only)

# Without Emotions {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/Face_Reader/The_Experiment/Regressions/b(t)-b(t-1)/b(t)-b(t-1)_with_t-1_record_stage_emotions.csv", header=TRUE, sep=",")

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```

# With All Emotions {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```

# Valence Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


# Neutrality Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```

# Happiness Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


# Sadness Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```

# Anger Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


# Surprise Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```

# Fear Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```

# Disgust Only {.tabset}

## All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))


```



## Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



## Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(bt_bt_1 ~ pt_pt_1 + bt_1_bt_2 + bt_1_pt_1 + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("p(t)-p(t-1)"= "pt_pt_1" ,"b(t-1)-b(t-2)" = "bt_1_bt_2", "b(t-1)-p(t-1)" = "bt_1_pt_1", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```