---
title: "Regressions results"
author: "(Using previous record stage emotions)"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
---


$B_{i,t}^{t+k} = C_{i} + \beta_1Periodtrend + \beta_2Markettrend + \beta_3Neutrality_{i,t-1} + \beta_4Happiness_{i,t-1} + \beta_5Sadness_{i,t-1} + \beta_6Anger_{i,t-1} + \beta_7Surprise_{i,t-1} + \beta_8Fear_{i,t-1} + \beta_9Disgust_{i,t-1}$
(Fixed effects regression model)
(Periods 2-15 only)

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
my_main_data <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/Face_Reader/The_Experiment/Regressions/p_m_trend_with_emotions_using_record_stage_emotions_of_t-1/S1_S6_transpose_with_t-1_record_stage_emotions.csv", header=TRUE, sep=",")
 
```

# HL

## Low HL (risk averse)

```{r, echo= FALSE, message=FALSE,warning = FALSE}

mydata <- subset(my_main_data, HL<=4)
 
```

### All Emotions {.tabset}

#### All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


#### Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



#### Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



### Valence Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Neutrality Only {.tabset}

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Happiness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Sadness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Anger Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Surprise Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Fear Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Disgust Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




## High HL (risk seeking

```{r, echo= FALSE, message=FALSE,warning = FALSE}

mydata <- subset(my_main_data, HL>4)
 
```

### All Emotions {.tabset}

#### All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


#### Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



#### Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



### Valence Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Neutrality Only {.tabset}

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Happiness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Sadness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Anger Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Surprise Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Fear Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Disgust Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




# CRT

## Low CRT (0 or 1)

```{r, echo= FALSE, message=FALSE,warning = FALSE}

mydata <- subset(my_main_data, CRT<=1)
 
```

### All Emotions {.tabset}

#### All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


#### Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



#### Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



### Valence Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Neutrality Only {.tabset}

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Happiness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Sadness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Anger Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Surprise Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Fear Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Disgust Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




## High CRT (2 or 3)

```{r, echo= FALSE, message=FALSE,warning = FALSE}

mydata <- subset(my_main_data, CRT>1)
 
```

### All Emotions {.tabset}

#### All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


#### Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



#### Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



### Valence Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Neutrality Only {.tabset}

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Happiness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Sadness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Anger Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Surprise Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Fear Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Disgust Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




# Gender

## Males

```{r, echo= FALSE, message=FALSE,warning = FALSE}

mydata <- subset(my_main_data, gender==0)
 
```

### All Emotions {.tabset}

#### All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


#### Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



#### Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



### Valence Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Neutrality Only {.tabset}

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Happiness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Sadness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Anger Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Surprise Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Fear Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Disgust Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




## Females

```{r, echo= FALSE, message=FALSE,warning = FALSE}

mydata <- subset(my_main_data, gender==1)
 
```

### All Emotions {.tabset}

#### All subjects

```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```


#### Traders only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



#### Observers only

```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral + happy + sad + angry + surprised + scared + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral" , "Happiness" = "happy", "Sadness" = "sad", "Anger" = "angry","Surprise" = "surprised", "Fear" = "scared", "Disgust" = "disgusted" ),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))

```



### Valence Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + valence, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + valence, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Valence" = "valence"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Neutrality Only {.tabset}

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + neutral, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + neutral, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Neutrality" = "neutral"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Happiness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + happy, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + happy, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Happiness" = "happy"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Sadness Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + sad, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + sad, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Sadness" = "sad"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Anger Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + angry, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + angry, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Anger" = "angry"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Surprise Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + surprised, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + surprised, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Surprise" = "surprised"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Fear Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + scared, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + scared, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Fear" = "scared"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




### Disgust Only {.tabset}

#### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



#### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


#### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + disgusted, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + disgusted, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2,scale = TRUE, digits=3,
             model.names = c("Market1", "Market2"),statistics = c(N = "nobs",Adj_R2 = "adj.r.squared", R2 = "r.squared") , coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend", "Disgust" = "disgusted"),error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


