---
title: "Regressions results"
author: "(Without emotions)"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---


$B_{i,t}^{t+k} = C_{i} + \beta_1Periodtrend + \beta_2Markettrend$

# All sessions – combined {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/Face_Reader/The_Experiment/panel_data/transposed_data/S1_S6_transpose.csv", header=TRUE, sep=",")

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```



Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Dummy variable
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend" ,"Dummy(Traders)" = "traders_1" ),error_format = "({p.value})")
```

Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

# Session 1 {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S1")
market2 = subset(market2, s_num == "S1")

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```



Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
market1 = subset(market1, s_num == "S1")
market2 = subset(market2, s_num == "S1")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
market1 = subset(market1, s_num == "S1")
market2 = subset(market2, s_num == "S1")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Dummy variable
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S1")
market2 = subset(market2, s_num == "S1")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend" ,"Dummy(Traders)" = "traders_1" ),error_format = "({p.value})")
```

Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

# Session 2 {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S2")
market2 = subset(market2, s_num == "S2")

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```



Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
market1 = subset(market1, s_num == "S2")
market2 = subset(market2, s_num == "S2")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
market1 = subset(market1, s_num == "S2")
market2 = subset(market2, s_num == "S2")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Dummy variable
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S2")
market2 = subset(market2, s_num == "S2")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend" ,"Dummy(Traders)" = "traders_1" ),error_format = "({p.value})")
```

Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

# Session 3 {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S3")
market2 = subset(market2, s_num == "S3")

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```



Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
market1 = subset(market1, s_num == "S3")
market2 = subset(market2, s_num == "S3")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
market1 = subset(market1, s_num == "S3")
market2 = subset(market2, s_num == "S3")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Dummy variable
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S3")
market2 = subset(market2, s_num == "S3")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend" ,"Dummy(Traders)" = "traders_1" ),error_format = "({p.value})")
```

Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

# Session 4 {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S4")
market2 = subset(market2, s_num == "S4")

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```



Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
market1 = subset(market1, s_num == "S4")
market2 = subset(market2, s_num == "S4")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
market1 = subset(market1, s_num == "S4")
market2 = subset(market2, s_num == "S4")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Dummy variable
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S4")
market2 = subset(market2, s_num == "S4")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend" ,"Dummy(Traders)" = "traders_1" ),error_format = "({p.value})")
```

Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

# Session 5 {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S5")
market2 = subset(market2, s_num == "S5")

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```



Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
market1 = subset(market1, s_num == "S5")
market2 = subset(market2, s_num == "S5")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
market1 = subset(market1, s_num == "S5")
market2 = subset(market2, s_num == "S5")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Dummy variable
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S5")
market2 = subset(market2, s_num == "S5")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend" ,"Dummy(Traders)" = "traders_1" ),error_format = "({p.value})")
```

Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

# Session 6 {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S6")
market2 = subset(market2, s_num == "S6")

#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```



Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
market1 = subset(market1, s_num == "S6")
market2 = subset(market2, s_num == "S6")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
market1 = subset(market1, s_num == "S6")
market2 = subset(market2, s_num == "S6")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend"),error_format = "({p.value})")
```


Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)

## Dummy variable
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
market1 = subset(market1, s_num == "S6")
market2 = subset(market2, s_num == "S6")
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k") , model="within")
#Random effect market 1
Random_effects1 = plm(belief ~ p_trend + traders_1, data=market1, index = c("id","t_k"), model="random")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k") , model="within")
#Random effect market 2
Random_effects2 = plm(belief ~ p_trend + m_trend + traders_1, data=market2, index = c("id","t_k"), model="random")

export_summs(Fixed_effects1, Random_effects1, Fixed_effects2,Random_effects2,scale = TRUE,
             model.names = c("(Market1) Fixed effects","(Market1) Random effects","(Market2) Fixed effects","(Market2) Random effects"),
             statistics = c(N = "nobs", R2 = "r.squared") , coefs =  c("Constant" = "(Intercept)", "Periodtrend" = "p_trend",
                                                                       "Markettrend" = "m_trend" ,"Dummy(Traders)" = "traders_1" ),error_format = "({p.value})")
```

Hausman Test - Market 1

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```

Hausman Test - Market 2

```{r, echo= FALSE, message=FALSE, warning=FALSE}
(hausma  = phtest(Fixed_effects1,Random_effects1))
```
(If the null is rejected, the Fixed effects method is chosen to model the data instead of the Random effects method)