---
title: "Period and Market trends"
author: "(Without emotions)"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---


$B_{i,t}^{t+k} = C_{i} + \beta_1Periodtrend + \beta_2Markettrend$

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
my_main_data <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/Face_Reader/The_Experiment/panel_data/transposed_data/S1_S6_transpose.csv", header=TRUE, sep=",")
 
```

# HL

## Low HL (risk averse) {.tabset}

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- subset(my_main_data, HL<=4)
 
```

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}


market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## High HL (risk seeking) {.tabset}

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- subset(my_main_data, HL>4)
 
```

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}


market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# CRT

## Low CRT (0 or 1) {.tabset}

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- subset(my_main_data, CRT<=1)
 
```

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}


market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## High CRT (2 or 3) {.tabset}

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- subset(my_main_data, CRT>1)
 
```

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}


market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Gender

## Males {.tabset}

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- subset(my_main_data, gender==0)
 
```

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}


market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Females {.tabset}

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
mydata <- subset(my_main_data, gender==1)
 
```

### All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}


market1 = subset(mydata, period<=15)
market2 = subset(mydata, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

traders  <- subset(mydata, traders_1==1)

market1 = subset(traders, period<=15)
market2 = subset(traders, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


### Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

Observers <- subset(mydata, traders_1==0)

market1 = subset(Observers, period<=15)
market2 = subset(Observers, period>15)
#Fix effect market 1
Fixed_effects1 = plm(belief ~ p_trend, data=market1, index = c("id","t_k") , model="within")
#Fix effect market 2
Fixed_effects2 = plm(belief ~ p_trend + m_trend, data=market2, index = c("id","t_k") , model="within")

export_summs(Fixed_effects1, Fixed_effects2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Periodtrend" = "p_trend","Markettrend" = "m_trend"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```

