---
title: "Relationship between predicted and actual price change between periods t-1 and t"
author: "(Without emotions)"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---


$P_{t}-P_{t-1} = \alpha + \beta(B_{t}^t-P_{t-1})$

# Without Emotions {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}
library(plm)
library(tidyverse)
library(jtools)
library(huxtable)
library(ggplot2)
library(ggpubr)

mydata <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/Face_Reader/The_Experiment/Regressions/p(t)-p(t-1)/S1_S6_transpose.csv", header=TRUE, sep=",")

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
plot1 = ggplot(market1, aes(x=belief_minus_price_t_minus_1, y=delta_price))+
  geom_point(shape = 21,color = "blue", size = 2) + 
  geom_hline(yintercept=0, linetype="dashed", color = "red", size=1) + 
  geom_vline(xintercept = 0, linetype="dashed", color = "red", size=1)+
  scale_x_continuous(name="B-P", limits=c(-46, 127)) +
  scale_y_continuous(name="P-P", limits=c(-249, 81))


plot2 = ggplot(market2, aes(x=belief_minus_price_t_minus_1, y=delta_price))+
  geom_point(shape = 21,color = "blue", size = 2) + 
  geom_hline(yintercept=0, linetype="dashed", color = "red", size=1) + 
  geom_vline(xintercept = 0, linetype="dashed", color = "red", size=1)+
  scale_x_continuous(name="B-P", limits=c(-46, 127))+
  scale_y_continuous(name="P-P", limits=c(-249, 81))

ggarrange(plot1, plot2, 
          labels = c("Market 1", "Market 2"),
          ncol = 2, nrow = 1)
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
plot1 = ggplot(market1, aes(x=belief_minus_price_t_minus_1_traders, y=delta_price))+
  geom_point(shape = 21,color = "blue", size = 2) + 
  geom_hline(yintercept=0, linetype="dashed", color = "red", size=1) + 
  geom_vline(xintercept = 0, linetype="dashed", color = "red", size=1)+
  scale_x_continuous(name="B-P", limits=c(-46, 127)) +
  scale_y_continuous(name="P-P", limits=c(-249, 81))


plot2 = ggplot(market2, aes(x=belief_minus_price_t_minus_1_traders, y=delta_price))+
  geom_point(shape = 21,color = "blue", size = 2) + 
  geom_hline(yintercept=0, linetype="dashed", color = "red", size=1) + 
  geom_vline(xintercept = 0, linetype="dashed", color = "red", size=1)+
  scale_x_continuous(name="B-P", limits=c(-46, 127))+
  scale_y_continuous(name="P-P", limits=c(-249, 81))

ggarrange(plot1, plot2, 
          labels = c("Market 1", "Market 2"),
          ncol = 2, nrow = 1)
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1_obs, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1_obs, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1_obs"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
plot1 = ggplot(market1, aes(x=belief_minus_price_t_minus_1_obs, y=delta_price))+
  geom_point(shape = 21,color = "blue", size = 2) + 
  geom_hline(yintercept=0, linetype="dashed", color = "red", size=1) + 
  geom_vline(xintercept = 0, linetype="dashed", color = "red", size=1)+
  scale_x_continuous(name="B-P", limits=c(-46, 127)) +
  scale_y_continuous(name="P-P", limits=c(-249, 81))


plot2 = ggplot(market2, aes(x=belief_minus_price_t_minus_1_obs, y=delta_price))+
  geom_point(shape = 21,color = "blue", size = 2) + 
  geom_hline(yintercept=0, linetype="dashed", color = "red", size=1) + 
  geom_vline(xintercept = 0, linetype="dashed", color = "red", size=1)+
  scale_x_continuous(name="B-P", limits=c(-46, 127))+
  scale_y_continuous(name="P-P", limits=c(-249, 81))

ggarrange(plot1, plot2, 
          labels = c("Market 1", "Market 2"),
          ncol = 2, nrow = 1)
```



# All Emotions {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_all + happy_all + sad_all + angry_all + surprised_all + scared_all + disgusted_all
, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_all + happy_all + sad_all + angry_all + surprised_all + scared_all + disgusted_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" , "Neutrality" = "neutral_all" , "Happiness" = "happy_all", "Sadness" = "sad_all", "Anger" = "angry_all","Surprise" = "surprised_all", "Fear" = "scared_all", "Disgust" = "disgusted_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1_traders + neutral_traders + happy_traders + sad_traders + angry_traders + surprised_traders + scared_traders + disgusted_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1_traders + neutral_traders + happy_traders + sad_traders + angry_traders + surprised_traders + scared_traders + disgusted_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1_traders", "Neutrality" = "neutral_traders" , "Happiness" = "happy_traders", "Sadness" = "sad_traders", "Anger" = "angry_traders","Surprise" = "surprised_traders", "Fear" = "scared_traders", "Disgust" = "disgusted_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1_obs + neutral_observers + happy_observers + sad_observers + angry_observers + surprised_observers + scared_observers + disgusted_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1_obs + neutral_observers + happy_observers + sad_observers + angry_observers + surprised_observers + scared_observers + disgusted_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1_obs", "Neutrality" = "neutral_observers" , "Happiness" = "happy_observers", "Sadness" = "sad_observers", "Anger" = "angry_observers","Surprise" = "surprised_observers", "Fear" = "scared_observers", "Disgust" = "disgusted_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Valence Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + valence_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + valence_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Valence" = "valence_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + valence_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + valence_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Valence" = "valence_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + valence_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + valence_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Valence" = "valence_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```




# Neutrality Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Neutrality" = "neutral_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Neutrality" = "neutral_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + neutral_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Neutrality" = "neutral_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Happiness Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + happy_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + happy_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Happiness" = "happy_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + happy_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + happy_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Happiness" = "happy_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + happy_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + happy_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Happiness" = "happy_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Sadness Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + sad_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + sad_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Sadness" = "sad_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + sad_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + sad_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Sadness" = "sad_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + sad_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + sad_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Sadness" = "sad_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Anger Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + angry_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + angry_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Anger" = "angry_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + angry_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + angry_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Anger" = "angry_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + angry_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + angry_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Anger" = "angry_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Surprise Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + surprised_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + surprised_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Surprise" = "surprised_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + surprised_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + surprised_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Surprise" = "surprised_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + surprised_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + surprised_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Surprise" = "surprised_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Fear Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + scared_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + scared_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Fear" = "scared_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + scared_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + scared_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Fear" = "scared_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + scared_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + scared_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Fear" = "scared_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```



# Disgust Only {.tabset}

## All subjects
```{r, echo= FALSE, message=FALSE, warning=FALSE}

market1 = subset(mydata,to_run_1==1)
market2 = subset(mydata,to_run_1==1)
market1 = subset(market1, period<=15)
market2 = subset(market2, period>15)
#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + disgusted_all, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + disgusted_all, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Disgust" = "disgusted_all"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Traders only
```{r, echo= FALSE, message=FALSE, warning=FALSE}



#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + disgusted_traders, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + disgusted_traders, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Disgust" = "disgusted_traders"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```


## Observers only
```{r, echo= FALSE, message=FALSE, warning=FALSE}

#OLS market 1
OLS1 = lm(delta_price ~ belief_minus_price_t_minus_1 + disgusted_observers, data=market1)
#OLS market 2
OLS2 = lm(delta_price ~ belief_minus_price_t_minus_1 + disgusted_observers, data=market2)

export_summs(OLS1, OLS2, digits = 4,
             model.names = c("Market1","Market2"),
             statistics = c(N = "nobs", Adj_R2 = "adj.r.squared", R2 = "r.squared") ,
            coefs =  c("Intercept" = "(Intercept)","X" = "belief_minus_price_t_minus_1" ,"Disgust" = "disgusted_observers"),
             error_format = "({p.value})", stars = c(`***` = 0.01, `**` = 0.05, `*` = 0.1))
```

